% ==========================================================
% Impact Statement
% ==========================================================

\chapter*{Impact Statement}
\addcontentsline{toc}{chapter}{Impact Statement}

\noindent

\textbf{Maastricht University Promotion Regulations.} \\
\textit{Annex 4. Article 12 paragraph 8.}

\vspace{1em}
The doctoral candidate must add an impact paragraph to the thesis of 500 to 2,000 words. This paragraph consists of a reflection in layman's terms (for a wide target group) on the scientific impact of the results of the research described in the thesis, and if applicable also the impact on society already achieved or expected.

\vspace{1em}
The impact paragraph forms part of the thesis and will be fully included in the consideration by the Assessment Committee and the Defense Committee when evaluating the thesis. If the impact of the results of the research is also discussed elsewhere in the thesis, the doctoral candidate can come back to it in the impact paragraph.

\vspace{1em}
In order to formulate the impact paragraph, four questions are provided that may serve as a guidance: \\

\vspace{1em}
1. (Research) What is the main purpose of the research described in the  thesis and what are the main results and conclusions? \\
2. (Relevance) What is the (potential) contribution of the results of this research to science, and if applicable to societal sectors and societal challenges? \\
3. (Target group) To whom are the research findings interesting and/or relevant? And why? \\
4. (Activity) In what way can these target groups be involved and informed about the research findings so that the knowledge gained can be used in the future? \\

\vspace{1em}
-- This is a placeholder text, make sure to replace with your own text --